Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-05-09 SupportingInformation.Rmd
rearranging figure
calling noise mat outside the function and then passing as input

<!--Another model, distinct from the above, Dan and Shya to discuss-->
```{r asym_sens_beta_variation, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"),mtime("bivfunctionplot.R"),mtime("CopulaFunctions_flexible.R"),mtime("copsurrog2d.R"))}
set.seed(seed)
source("asym_sensitivity.R")

#-----------------------------------------------------------------------------------
# This function takes 
# Input :
#       N : number of global and local noise points you want
#       rho : covariance of global noise matrix
#       alpha : a number : local noise coeeficient
#       beta : growth factor of pop
#       decrease : logical (controls the nature of global noise)
#       numkeep_last : number of points you want to keep for the pop matrix from the end
#       ploton : logical for optional plot

@@

plotter_asym_sens_beta_varn<-function(N,rho,alpha,beta,numkeep_last,ploton){

  pop<-Simulator_asym_sens(N=N,rho=rho,alpha=alpha,beta=beta,p0=c(0,0),decrease=F,numkeep_last=numkeep_last)
  pop_d<-Simulator_asym_sens(N=N,rho=rho,alpha=alpha,beta=beta,p0=c(0,0),decrease=T,numkeep_last=numkeep_last)

  neg_beta<- -beta
  pop_neg_beta<-Simulator_asym_sens(N=N,rho=rho,alpha=alpha,beta=neg_beta,p0=c(0,0),decrease=F,numkeep_last=numkeep_last)
  pop_d_neg_beta<-Simulator_asym_sens(N=N,rho=rho,alpha=alpha,beta=neg_beta,p0=c(0,0),decrease=T,numkeep_last=numkeep_last)

@@

}
#--------------------------------------------------------------
N<-10000
rho<-0.8
alpha<-0.2
numkeep_last<-1000

pdf("./Results/asym_sens_results/beta_0.1_asym_sens.pdf")
ans_beta_0.1<-plotter_asym_sens_beta_varn(N=N,rho=rho,alpha=alpha,beta=0.1,numkeep_last=numkeep_last,ploton=T)
dev.off()

pdf("./Results/asym_sens_results/beta_0.9_asym_sens.pdf")
ans_beta_0.9<-plotter_asym_sens_beta_varn(N=N,rho=rho,alpha=alpha,beta=0.9,numkeep_last=numkeep_last,ploton=T)
dev.off()

@@

\newpage
# References
<div id="refs"></div>

>>>>

<!--Another model, distinct from the above, Dan and Shya to discuss-->
```{r asym_sens_beta_variation, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"),mtime("bivfunctionplot.R"),mtime("CopulaFunctions_flexible.R"),mtime("copsurrog2d.R"))}
set.seed(seed)
#-----------------------------------------------------------------------------------
source("OurBiCopSelect.R")
source("bivfunctionplot.R")
source("asym_sensitivity.R")
#-----------------------------------------------------------------------------------
# This function takes 
# Input :
#       mg : global noise matrix (dim = N by 2)
#       ml : local noise matrix (dim = N by 2)
#       alpha : a number : local noise coeeficient
#       beta : growth factor of pop
#       decrease : logical (controls the nature of global noise)
#       numkeep_last : number of points you want to keep for the pop matrix from the end
#       ploton : logical for optional plot

@@

plotter_asym_sens_beta_varn<-function(mg,ml,alpha,beta,numkeep_last,ploton){

  pop<-Simulator_asym_sens(mg=mg,ml=ml,alpha=alpha,beta=beta,p0=c(0,0),decrease=F,numkeep_last=numkeep_last)
  pop_d<-Simulator_asym_sens(mg=mg,ml=ml,alpha=alpha,beta=beta,p0=c(0,0),decrease=T,numkeep_last=numkeep_last)

  neg_beta<- -beta
  pop_neg_beta<-Simulator_asym_sens(mg=mg,ml=ml,alpha=alpha,beta=neg_beta,p0=c(0,0),decrease=F,numkeep_last=numkeep_last)
  pop_d_neg_beta<-Simulator_asym_sens(mg=mg,ml=ml,alpha=alpha,beta=neg_beta,p0=c(0,0),decrease=T,numkeep_last=numkeep_last)

@@

}
#----------------------------------------------------------
N<-10000
rho<-0.8
alpha<-0.2
numkeep_last<-1000
temp<-get_noise_glob_loc_mat(N=N,rho=rho)
mg<-temp$mg
ml<-temp$ml

pdf("./Results/asym_sens_results/beta_0.1_asym_sens.pdf")
ans_beta_0.1<-plotter_asym_sens_beta_varn(mg=mg,ml=ml,alpha=alpha,beta=0.1,numkeep_last=numkeep_last,ploton=T)
dev.off()

pdf("./Results/asym_sens_results/beta_0.9_asym_sens.pdf")
ans_beta_0.9<-plotter_asym_sens_beta_varn(mg=mg,ml=ml,alpha=alpha,beta=0.9,numkeep_last=numkeep_last,ploton=T)
dev.off()

@@

# References
<div id="refs"></div>
